Algebraic File Synchronization: Adequacy and Completeness

### 2016-10-18 p2/ordering.tex
Stronger lemma about distant pairs

In \cref{simple_reorder_equiv} we offer a formal proof that $\orderset{U}$ meets our expectations.
It is an important property of simple sequences: namely, that
all of their valid reorderings are equivalent,
and all equivalent sequences are mere reorderings.
To prove this, we will need the following results:

\begin{mylem}\label{order_is_only_possible}
For any simple sequence $S$ and its permutation $T$, 
\[ T\not\in\orderset{S} \Longrightarrow T\equiv\cbrk. \]
\end{mylem}
\begin{proof}
$T$ can only be excluded from $\orderset{S}$ if it contains commands on a node and its parent
which violate the conditions in \cref{def_orderset},
which, as simple sequences do not contain assertion commands,
entails that those commands placed next to each other in the same order
would not form a construction or destruction pair.

Informally speaking,
our proposition for simple sequences $T\nequiv\cbrk$ is equivalent to the statement that
two commands on a node and its parent must form
a construction or destruction pair even if they are not next to each other.
This is true because in simple sequences
there cannot be another command between either of the nodes involved,
so if the commands are incompatible, no command between them can change that.

% BACK_TO_THE_FS TODO
% TODO Review any proof depending on "nothing changes FS at n until...".
To prove our proposition formally, we reach back to our filesystem model.
Select two commands in $T$ that do not conform to \cref{def_orderset}, $\cxynv$ and $\czwmv$,
and split $T$ around them into three parts:
\[ T = T_0 \cc \cxynv \cc T_1 \cc \czwmv \cc T_2 \]
As $T$ is simple, there cannot be any commands on $n$ or $m$ in $T_1$,
and therefore $(T_0\cc\cxynv\cc T_1)\FS(n) = y$.
If $n=\parent(m)$, then we know $y\neq\vald$, and
(similarly to the reasoning in \cref{ax_directchild_breaks})
as either before or after $\czwmv$ which is not an assertion command,
$\FS(m)\neq\empt$, the latter command will break the filesystem.
If $\parent(n)=m$, then we know $y\neq\empt$, and
(similarly to the reasoning in \cref{ax_directparent_breaks})
as wither before or after $\czwmv$, $\FS(m)\neq\vald$,
the latter command will break the filesystem.
\end{proof}

>>>>

In \cref{simple_reorder_equiv} we offer a formal proof that $\orderset{U}$ meets our expectations.
It is an important property of simple sequences: namely, that
all of their valid reorderings are equivalent,
and all equivalent sequences are mere reorderings.
To prove this, we will need the following results.

\begin{mylem}\label{simple_distant_pairs}
For any simple sequence $S\nequiv\cbrk$
if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
then $\cxynv\cc\czwmv\nequiv\cbrk$.
\end{mylem}
\begin{proof}
As usual, by subsequence we mean a subset of the commands in $S$ in the same order as they are found in $S$.

Informally speaking, the proposition means that
the two commands must form a construction or destruction pair even
if they are not next to each other.
This is true because in simple sequences
there cannot be another command on $n$ or $m$,
so if the commands are incompatible, no command between them can change that.
In fact, this \namecref{simple_distant_pairs} is the general case
of \cref{ax_directchild_breaks,ax_directparent_breaks}.

% BACK_TO_THE_FS TODO
% TODO Review any proof depending on "nothing changes FS at n until...".
Formally, we prove our proposition by contradiction,
and in this version of the proof we reach back to our filesystem model.
We assume $S\nequiv\cbrk$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
but it contains commands that do not form a construction or destruction pair.
Select two such commands, $\cxynv$ and $\czwmv$,
and split $S$ around them into three parts:
\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2 \]
As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.

If $n=\parent(m)$, then 
we know $(S_0\cc\cxynv\cc S_1)\FS(n) = y$, and as $[z]\neq[w]$, either
$[(S_0\cc\cxynv\cc S_1)\FS(m)]=[z]\neq[\empt]$,
or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\FS(m)]=[w]\neq[\empt]$.
Therefore $y$ must be $\vald$, as otherwise the tree property would be violated
when applying $\czwmv$,
and $[x]\neq[\vald]$ as $\cxynv$ is not an assertion command.
As $[S_0\FS(n)]=[x]\neq[\vald]$, we know
$S_0\FS(m)=\empt$ as otherwise the tree property would be violated.
Therefore $[S_0\FS(m)]=[z]=[\empt]$, which, combined with $y=\vald$
means that $\cxynv\cc\czwmv\nequiv\cbrk$ is a construction pair, which is a contradiction.

If $\parent(n)=m$, then 
as $(S_0\cc\cxynv\cc S_1)\FS(n) = y$, and either
$[(S_0\cc\cxynv\cc S_1)\FS(m)]=[z]\neq[\vald]$
or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\FS(m)]=[w]\neq[\vald]$,
$y$ must be $\empt$, and $[x]\neq[\empt]$.
As $[S_0\FS(n)]=[x]\neq[\empt]$, we know $S_0\FS(m)=\vald$.
Therefore $[S_0\FS(m)]=[z]=[\vald]$, which, combined with $y=\empt$
means that $\cxynv\cc\czwmv\nequiv\cbrk$ is a destruction pair, which is a contradiction.
\end{proof}

\begin{mylem}\label{order_is_only_possible}
For any simple sequence $S$ and its permutation $T$, 
\[ T\not\in\orderset{S} \Longrightarrow T\equiv\cbrk. \]
\end{mylem}
\begin{proof}
TODO corollary
\end{proof}
